### 2019-09-04 paper/HOLMultivariate.tex
The new substitution syntax (learnt from HOL's lambda example)

\newcommand{\HOLMultivariateDate}{03 Settembre 2019}
\newcommand{\HOLMultivariateTime}{14:31}

@@

       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es})

@@

       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})

@@

            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})

@@

            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})

@@

       \HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
       \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=}
        \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}. \HOLConst{CCS_Subst} \HOLBoundVar{e} \HOLBoundVar{y} \HOLBoundVar{x}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))

@@

       \HOLConst{IS_PROC} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})

@@

       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es}) \HOLBoundVar{C})

@@

       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})

@@

           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}}
           (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
           (\HOLConst{CCS_SUBST} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLBoundVar{X})

@@

       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X}

@@

       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C})

@@

       \HOLConst{DISJOINT} (\HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{X}. \HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{FDOM} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})

@@

\HOLTokenTurnstile{} ([] \HOLSymConst{\HOLTokenMapto{}} []) \HOLSymConst{=} \HOLConst{FEMPTY}

@@

       ((\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})

@@

       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})

@@

       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})

@@

       ((\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} (\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{ys}) \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))

@@

       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}

@@

           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{OBS_CONGR} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})

@@

           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{OBS_contracts} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})

@@

           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{STRONG_EQUIV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})

@@

               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}

@@

                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}

@@

                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E\sp{\prime}}

@@

                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                    \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}

@@

                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}

@@

               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
                     (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})

@@

       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys}) \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}

@@

                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}}

@@

       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}

@@

           \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Qs}) \HOLBoundVar{C}

>>>>

\newcommand{\HOLMultivariateDate}{04 Settembre 2019}
\newcommand{\HOLMultivariateTime}{10:49}

@@

       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})

@@

       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}) \HOLBoundVar{E})

@@

            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})

@@

            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})

@@

       \HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}. [\HOLBoundVar{y}/\HOLBoundVar{x}] \HOLBoundVar{e}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))

@@

       \HOLConst{IS_PROC} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})

@@

       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) \HOLSymConst{=} [\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})

@@

       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})

@@

           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
           ([\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}/\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{P}/\HOLBoundVar{X}] \HOLBoundVar{E\sp{\prime}})

@@

       ([\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{E\sp{\prime}}/\HOLBoundVar{X}] \HOLBoundVar{E}

@@

       \HOLConst{context} \HOLBoundVar{Xs} ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})

@@

       \HOLConst{DISJOINT} (\HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{X}. \HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
       (\HOLConst{FDOM} (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})

@@

\HOLTokenTurnstile{} \HOLConst{fromList} [] [] \HOLSymConst{=} \HOLConst{FEMPTY}

@@

       (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})

@@

       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})

@@

       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})

@@

       (\HOLConst{fromList} (\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}) (\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))

@@

       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_CONGR} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_contracts} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{STRONG_EQUIV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})

@@

               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}

@@

                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}

@@

                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}

@@

                [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}

@@

                      ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}

@@

               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})

@@

       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}

@@

                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}

@@

       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}

@@

           [\HOLBoundVar{E} \HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}

@@

                   [\HOLBoundVar{E} \HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}
